Hydras \& Co.

### 2022-02-17 doc/gaia-chapter.tex
small corrections

The following cancel lemmas will be often used in order to simplify sub-terms of the form \texttt{g2h (h2g {\it t})} and \texttt{h2g (g2h {\it t})} which appear in many proofs by rewriting.

@@

%%% ICI

\subsection{Examples of refinements}
Both of our libraries define constants like $0$, $1$, $\omega$, and arithmetic functions: successor, addition, multiplication, and exponential of base $\omega$ (function $\phi_0$). We prove consistency of these definitions. Finally, we prove that the boolean predicates `` to be in normal form'' are equivalent.

@@

@@

 \inputsnippets{GaiaToHydra/distributivity}.

We plan to automatize the most as possible this transfer of lemmas in this direction.

>>>>

The following cancel lemmas will be often used in order to simplify sub-terms of the form (\texttt{g2h (h2g {\it t})}) and (\texttt{h2g (g2h {\it t})}) which appear in many proofs by rewriting.

@@

\subsection{Examples of refinement}
Both of our libraries define constants like $0$, $1$, $\omega$, and arithmetic functions: successor, addition, multiplication, and exponential of base $\omega$ (function $\phi_0$). We prove that these definitions are mutually consistent. Finally, we prove that the boolean predicates `` to be in normal form'' are equivalent.

@@

\subsection{Looking for a lemma}
\coq's command \texttt{Search} and notation scopes allow you to explore both libraries.

\inputsnippets{T1Bridge/SearchDemo}

@@

 \inputsnippets{GaiaToHydra/distributivity}

We plan to automatize as soon as possible this kind of transfer of lemmas from \gaia to \HydrasLib.
